---
title: "plot_formant.rmd"
author: "Jojo Hu"
date: "10/6/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
# Plot model talkers' vowel space
```{r, include = F}
library(dplyr)

read_normed <- 
  function (file) {
    file_name <- basename(file)
    file_name <- str_extract(file_name, "\\S+(?=.csv?)")
    
    file <- read.csv(file, skip = 2)
    file[, "name"] <- file_name
    
    return (file)
    }

```

```{r, include = F}
library(ggplot2)
library(stringr)
library(dplyr)

# TO DO: Automate conversion from norm.txt to norm.csv and Delete the first two lines in the norm.csv files 

plot_formant <- 
  function (pattern) {
    
spB <-
  list.files(path = "/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-extract/",
             pattern = pattern, full.names = T)

if (pattern == "*norm.csv") {
  spB <- lapply(spB, read_normed)
  } else {
    spB <- lapply(spB, read.csv)
  }

spB <- do.call(rbind, spB)


return(spB)
  }

spB <- plot_formant("*norm.csv")

spB$part_id <- str_extract(spB$name, "\\S+(?=_r)|rsr_orig|new_speaker")
spB$task <- str_extract(spB$name, "rsr\\S{1}|rsr_orig|new_speaker")

spB[which(str_detect(spB$part_id, "blast")), "group"] <- "TD"
spB[which(str_detect(spB$part_id, "spoli")), "group"] <- "ASD"
spB[which(str_detect(spB$name, "rsr_orig")), "group"] <- "control"
spB[which(str_detect(spB$name, "new_speaker")), "group"] <- "high"
```

```{r}

spB <-
spB %>%
    filter(stress == 1, 
           !vowel %in% c("AY", "AW", "OY", "ER"),
           !word %in% c("TO", "US", "ON")) %>%
    mutate(word = tolower(word))


spB$vowel <- factor(spB$vowel, levels = c("IY", "IH", "EY", "EH",  
                                     "AA", "AO", "OW", "UH", "UW", "AH", "AE"))


spB_norm <- plot_formant("*norm.csv")



spB_dip <-
spB_norm %>%
    filter(stress == 1) %>%
    mutate(word = tolower(word))


spB_norm <-
spB_norm %>%
    filter(stress == 1, 
           !vowel %in% c("AY", "AW", "OY", "ER"),
           !word %in% c("TO", "US", "ON")) %>%
    mutate(word = tolower(word))


spB_norm$vowel <- factor(spB_norm$vowel, levels = c("IY", "IH", "EY", "EH", 
                                     "AA", "AO", "OW", "UH", "UW", "AH", "AE"))

unique(spB_norm$name)
```





```{r}
# Plotting Unnormed Vowel Space
spB[which(!spB$group == "ASD"),] %>%
ggplot(aes(x = norm_F2, y = norm_F1, color = vowel)) + 
    geom_point() + 
    scale_x_reverse() + scale_y_reverse() +
    theme_classic() + 
  facet_grid(~group+task)

spB[which(spB$group == "TD"),] %>%
ggplot(aes(x = norm_F2, y = norm_F1, color = vowel)) + 
    geom_point() + 
    scale_x_reverse() + scale_y_reverse() +
    theme_classic() + 
  facet_grid(~group+task)

spB[which(!spB$group == "TD"),] %>%
ggplot(aes(x = norm_F2, y = norm_F1, color = vowel)) + 
    geom_point() + 
    scale_x_reverse() + scale_y_reverse() +
    theme_classic() + 
  facet_grid(~group+task)

spB[which(spB$group == "ASD"),] %>%
ggplot(aes(x = norm_F2, y = norm_F1, color = vowel)) + 
    geom_point() + 
    scale_x_reverse() + scale_y_reverse() +
    theme_classic() + 
  facet_grid(~group+task)
```

# Plot line plots of formants
```{r}
library(ggplot2)
library(stringr)
library(reshape)
# Clean up here:
spB_dip[which(str_detect(spB_dip$name, "blast")), "group"] <- "TD"
spB_dip[which(str_detect(spB_dip$name, "spoli")), "group"] <- "ASD"

normCol <- colnames(spB_dip)[which(str_detect(colnames(spB_dip), "norm_\\S{2}."))]

normF <- spB_dip[,c("name", "vowel", "stress", "group", normCol)]

normFL <- melt(normF, id.vars = c("name", "group", "vowel", "stress"))

normFL$percentage <- str_extract(normFL$variable, "(?<=norm_\\S{2})\\S+(?=.)")

normFL$speaker <- str_extract(normFL$name, "\\S+(?=_output_norm)")

normFL$formant <- str_extract(normFL$variable, "(?<=_)\\S{2}(?=.?)")


linePlotMean <- list()

for (i in 1:length(unique(normFL$vowel))) {
  selected_vowel <- unique(normFL$vowel)[i]
linePlotMean[[i]] <-
    normFL %>%
  filter(vowel == selected_vowel) %>%
  ggplot(aes(x = percentage, y = value, color = vowel, group = vowel)) +
  geom_point() +
  geom_line(stat ="summary", fun.y = "mean") +
  facet_grid(~formant+group)
}

linePlotMean
```


# Plot clustered normed F1 and F2
```{r}
# Clean up here:
spB_norm[which(str_detect(spB_norm$name, "blast")), "group"] <- "TD"
spB_norm[which(str_detect(spB_norm$name, "spoli")), "group"] <- "ASD"
spB_norm[which(str_detect(spB_norm$name, "rsr_orig")), "group"] <- "control"
spB_norm[which(str_detect(spB_norm$name, "new_speaker")), "group"] <- "high"

ggplot(spB_norm, aes(x = norm_F2, y = norm_F1, color = vowel, label = vowel)) + 
    geom_point(alpha = 0.5) + 
    stat_ellipse() + 
    scale_x_reverse() + scale_y_reverse() + 
    scale_color_discrete(breaks = c("IY", "IH", "EY", "EH", "AE", 
                                     "AA", "AO", "OW", "UH", "UW", "AH")) +
  scale_color_discrete(breaks = c("IY", "IH", "EY", "EH", "AE", 
                                     "AA", "AO", "OW", "UH", "UW", "AH")) +
  facet_grid(~group) +
  theme_classic()


# ggsave("f1_f2.png",bg="transparent",width = 30, height = 15, units = "cm")
```

# Compare duration of speakers
```{r, include = F}
library(dplyr)

senDur <- read.csv("/Users/jojohu/Documents/Time/stimuli/rsr_stim/sentence_duration.csv")

senDur$duration <- senDur$end - senDur$begin

senDur %>%
  filter(!sound == "sp") %>%
  group_by(speaker) %>%
  dplyr::summarise(sum = sum(duration))
```




Plot the mean unnormed F1 and F2 of each model talker
```{r, eval = F, include = F}
library(reshape)

spB$name <- as.factor(spB$name)
spB$vowel <- as.factor(spB$vowel)

means <-
  spB %>%
    group_by(name,vowel) %>%
    dplyr::summarise(mean_F1 = mean(F1),
              mean_F2 = mean(F2)) 

mFormant <- data.frame(means)

mFormant <- melt(mFormant, by = c("name", "vowel"))

cast(mFormant, variable+vowel~name)
```


```{r, eval = F, include = F}
library(ggplot2)
ggplot(means, aes(x = mean_F2, y = mean_F1, label = vowel)) + 
    geom_label(size = 3, alpha = 0.5) + 
    # scale_shape_manual(values=1:nlevels(means$vowel)) +
    scale_x_reverse() + scale_y_reverse() +
    theme_classic() + 
  facet_grid(~name)

```


# Match sentence number (need to use ELAN instead)
```{r}
rowDiffT <- 
  spB %>% 
    group_by(part_id, task) %>%
    mutate(difference=beg-lag(beg,default=first(beg)))

# Only running this for control model talker condition

rowDiffTC <- rowDiffT[which(str_detect(rowDiffT$part_id, "spoli_c|blast_c") & rowDiffT$task =="rsr1"),]

rowDiffTModel <- rowDiffT[which(str_detect(rowDiffT$part_id, "rsr_orig")),]

estimateSen <- function(DF, second) {
    n = 0
    cDF <- list()
    for(i in 1:length(unique(DF$part_id))) {
      n = n + 1
      currentDF <- DF[which(DF$part_id == unique(DF$part_id)[i]),]
      currentDF[which(currentDF$difference > second), "sentence_estimate"] <- 
        seq(from = 2, to = length(which(currentDF$difference > second)) + 1)
      
      currentDF$sentence_estimate[1] <- 1
      
      cDF[[n]] <- currentDF
    }
  return(cDF)
}

rowDiffTC <- do.call(rbind, estimateSen(rowDiffTC, 5))
rowDiffTModel <- do.call(rbind, estimateSen(rowDiffTModel, 5))

rowDiffT <- rbind(rowDiffTC, rowDiffTModel)

rowDiffT <- 
  rowDiffT %>% 
    tidyr::fill(sentence_estimate)
```


```{r}
formantV <- read.csv("/Users/jojohu/Documents/Time/stimuli/word_vowel_examplars.csv")
demo <- read.csv("/Users/jojohu/Documents/Qlab/blast_online_data/demographic_data/online_demo_all.csv")[c("part_id", "group", "gender", "age_at_web_month", "age_at_web_year")]
rsr1Score <- read.csv("/Users/jojohu/Documents/Qlab/blast_online_data/RSR Online Home Scores  - blast scores (rsr_rsr1).csv")[c("participant.id", "raw.score", "standard")]
rsr1ScoreSpoli <- read.csv("/Users/jojohu/Documents/Qlab/blast_online_data/RSR Online Home Scores  - spoli scores (rsr_rsr1).csv")[c("participant.id", "raw.score", "standard")]

rsr1Score <- rbind(rsr1Score, rsr1ScoreSpoli)

formantV <- formantV[which(formantV$arphabet %in% c("IH", "IY", "EH", "AE", "AA", "AH", "UH", "UW", "AO")),]

arphabetVowel <- unique(formantV[,c("vowel", "arphabet")])

formantDF <- rowDiffT[which(rowDiffT$word %in% unique(formantV$praat_word)),]

formantDF <- formantDF[which(formantDF$vowel %in% c("IH", "IY", "EH", "AE", "AA", "AH", "UH", "UW", "AO")),]

formantDF <- merge(formantDF, demo, all.x = T)

formantDF[which(formantDF$part_id == "blast_c_488"), "gender"] <- "M"
formantDF[which(formantDF$part_id == "blast_c_488"), "age_at_web_year"] <- 8.55
formantDF[which(formantDF$part_id == "blast_c_488"), "age_at_web_month"] <- 8.55*12

formantDF[which(formantDF$part_id == "spoli_c_617"), "gender"] <- "M"
formantDF[which(formantDF$part_id == "spoli_c_617"), "age_at_web_year"] <- 7.89
formantDF[which(formantDF$part_id == "spoli_c_617"), "age_at_web_month"] <- 7.89*12


formantDF <- merge(formantDF, rsr1Score, by.x = "part_id", by.y = "participant.id", all.x = T)

colnames(formantDF)[which(colnames(formantDF) == "vowel")] <- "arphabet"

formantDF <- merge(formantDF, arphabetVowel, all.x = T)

# formantDF <- formantDF[-which(is.na(formantDF$vowel)),]
vowelInDF <- 
formantDF %>%
  group_by(vowel, word) %>%
  summarise_each(funs(mean), norm_F1, norm_F2)

vowelInDF <- vowelInDF[,c("vowel", "word")]

# write.csv(vowelInDF, "vowel_list.csv")

formantDF %>%
  group_by(group, gender) %>%
  summarise(Mean = round(mean(age_at_web_year), 2), SD = round(sd(age_at_web_year), 2), Min = round(min(age_at_web_year), 2), Max = round(max(age_at_web_year), 2), N = length(unique(part_id)))

t.test(formantDF[which(formantDF$group == "ASD"), "age_at_web_year"], formantDF[which(formantDF$group == "TD"), "age_at_web_year"])

vowelCountSubj <- 
formantDF %>%
  group_by(group, vowel) %>%
  summarise(mean(norm_F1), mean(norm_F2), N = n(), Nsuj = length(unique(part_id)), NtokenPerSubj = N/Nsuj)

# write.csv(vowelCountSubj, "vowelCountSubj.csv")

 # write.csv(ageDescrip, "age.csv")
```


# Calculate Euclidean Distance to Model Talker (squareroot((wordmodel’s F1 - wordparticipant’s F1)2 + (wordmodel’s F2 - wordparticipant’s F2)2)
```{r}
formantDFM <- formantDF[which(formantDF$part_id == "rsr_orig"),]
formantDFC <- formantDF[which(str_detect(formantDF$part_id, "blast|spoli")),]

# Add a column for actual sentence number in the list for children, so sentence number can be matched to model talker
# Now, the mean of duplicated words of model talker across sentences are extracted to do the comparison, not recommended:
formantDFM_mean <- 
formantDFM %>%
  group_by(word) %>%
   summarise_each(funs(mean), norm_F1, norm_F2)

distance <- list()
n = 0

for(i in 1:nrow(formantDFC)) {
  n = n + 1
      childWord <- formantDFC[i,]$word
      childSen <- formantDFC[i,]$sentence_estimate
      childF1 <- formantDFC[i,]$norm_F1
      childF2 <- formantDFC[i,]$norm_F2
      
      modelF1 <- formantDFM_mean[which(formantDFM_mean$word == childWord 
                                       # & formantDFM_mean$sentence_estimate == childSen
                                       ),]$norm_F1
      modelF2 <- formantDFM_mean[which(formantDFM_mean$word == childWord 
                                       # & formantDFM_mean$sentence_estimate == childSen
                                       ),]$norm_F2
    
      
      distanceTemp <- sqrt((modelF1 - childF1)^2 + (modelF2 - childF2)^2)
      
      if(length(modelF1) == 0 | length(modelF2) == 0) {
        distanceTemp <- NA
      }
     
      
      distance[[n]] <- distanceTemp
      print(paste(i, distanceTemp))
}

formantDFC$distance <- do.call(rbind, distance)



formantDFC <- 
  formantDFC %>% 
  group_by(part_id, vowel)  %>% 
        arrange(
          part_id,
          vowel,
            sentence_estimate
        ) %>%
  mutate(order = row_number())


formantDFC$sentence_estimate <- as.numeric(as.character(formantDFC$sentence_estimate))
formantDFC$order <- as.numeric(as.character(formantDFC$order))

meanDistance <-
formantDFC %>% 
  group_by(group, vowel)  %>% 
  summarise(mean(distance, na.rm = T))

# write.csv(meanDistance, "meanDistance.csv")

library(lmerTest)
m1 <- lmer(distance ~  group*order + age_at_web_month + (order|vowel), data = formantDFC)
summary(m1)

m2 <- lmer(distance ~  group*order*vowel + (1|part_id), data = formantDFC)
summary(m2)

cor.test(formantDFC$distance, formantDFC$age_at_web_month)
cor.test(formantDFC[which(formantDF$group == "ASD"),]$distance, formantDFC[which(formantDF$group == "ASD"),]$age_at_web_month)
cor.test(formantDFC[which(formantDF$group == "TD"),]$distance, formantDFC[which(formantDF$group == "TD"),]$age_at_web_month)

```


```{r}
formantDFC %>%
   filter(group == "ASD") %>%
  ggplot(aes(x = order, y = distance, color = vowel)) +
  geom_line(stat ="summary", fun.y = "mean") +
  labs(title = paste("Euclidean Distance Change Across Repetitions in children with ASD"),
         y = "Mean Euclidean Distance",  # Change x-axis label
         x = "Order of Vowel Occurrence") +
    theme(plot.title = element_text(hjust = 0.3)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

ggsave("asd_distance.png", dpi = 150)

formantDFC %>%
   filter(group == "TD") %>%
  ggplot(aes(x = order, y = distance, color = vowel)) +
  geom_line(stat ="summary", fun.y = "mean") +
  labs(title = paste("Euclidean Distance Change Across Repetitions in TD children"),
         y = "Mean Euclidean Distance",  # Change x-axis label
         x = "Order of Vowel Occurrence") +
    theme(plot.title = element_text(hjust = 0.3)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

ggsave("td_distance.png", dpi = 150)
```


```{r}

library(dplyr)
plotDistance <- list()

for (i in 1:length(unique(formantDFC$vowel))) {
  selected_vowel <- unique(formantDFC$vowel)[i]
plotDistance[[i]] <-
  formantDFC %>%
  filter(vowel == selected_vowel) %>%
  ggplot(aes(x = order, y = distance, color = group)) +
  geom_point() +
  # geom_line(stat ="summary", fun.y = "mean") +
   stat_summary(fun.data=formantDFC) + 
  geom_smooth(method='lm', formula= y~x) +
  labs(title = paste("Euclidean Distance Change Across Productions of", selected_vowel),
         y = "Mean Euclidean Distance",  # Change x-axis label
         x = "Order of Vowel Production") +
    theme(plot.title = element_text(hjust = 0.3)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) + 
      scale_x_continuous(breaks=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14))
}

for (i in 1:length(plotDistance)) {
  ggsave(paste0(i, ".png"), plot = plotDistance[[i]], dpi = 100)
}



```


# Plot Vowel Space with Mean Formants
```{r}
formantMean <-
  formantDF %>%
    group_by(part_id, group, gender, vowel) %>%
    filter(!(abs(norm_F1 - mean(norm_F1)) > 3*sd(norm_F1))) %>%
    filter(!(abs(norm_F2 - mean(norm_F2)) > 3*sd(norm_F2))) %>%
  summarise_each(funs(mean), norm_F1, norm_F2)

print(formantMean)

formantMean[which(formantMean$group == "TD"),] %>%
  ggplot(aes(x = norm_F2, y = norm_F1)) + 
      geom_label(aes(label = vowel, color = vowel), size = 5, alpha = 0.5, show.legend = FALSE) + 
      scale_x_reverse() + scale_y_reverse() +
      theme_classic() + 
    labs(title = "Vowel Space of TD Children",
         x = "Mean F2 (Hz)",  # Change x-axis label
         y = "Mean F1 (Hz)") +
    theme(plot.title = element_text(hjust = 0.3)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

ggsave("td_vowel_space.png", width = 10, height = 8)


formantMean[which(formantMean$group == "ASD"),] %>%
  ggplot(aes(x = norm_F2, y = norm_F1)) + 
      geom_label(aes(label = vowel, color = vowel), size = 5, alpha = 0.5, show.legend = FALSE) + 
      scale_x_reverse() + scale_y_reverse() +
      theme_classic() + 
    labs(title = " Vowel Space of Children with ASD",
         x = "Mean F2 (Hz)",  # Change x-axis label
         y = "Mean F1 (Hz)") +
    theme(plot.title = element_text(hjust = 0.3)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

ggsave("asd_vowel_space.png", width = 10, height = 8)



formantMean[which(formantMean$group == "control"),] %>%
  ggplot(aes(x = norm_F2, y = norm_F1)) + 
      geom_label(aes(label = vowel, color = vowel), size = 5, alpha = 0.5, show.legend = FALSE) + 
      scale_x_reverse() + scale_y_reverse() +
      theme_classic() + 
    labs(title = " Vowel Space of the Model Talker",
         x = "Mean F2 (Hz)",  # Change x-axis label
         y = "Mean F1 (Hz)") +
    theme(plot.title = element_text(hjust = 0.3)) +
  theme(
        plot.title = element_text(size=16, face="bold"),
        axis.title.x = element_text(size=14, face="bold"),
        axis.title.y = element_text(size=14, face="bold"),
        axis.text=element_text(size=12, face = "bold")
        ) +
  theme(legend.text=element_text(size=14, face="bold"),
        legend.title=element_text(size=15, face="bold")) +
   theme(
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

ggsave("model_vowel_space.png", width = 10, height = 8)

```






# Data Prep for plotting pitch
```{r}
# Read in prosody pro output

pList <- list.files(path = "/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align/", 
                    pattern = "*\\.f0$|.normtimef0$")

pList <- as.character(pList)

library(stringr)

newName <- paste0(pList, ".txt")

file.copy(from = file.path("/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align/", pList),
                      to = file.path("/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align/", newName))

pitchF <-  list.files(path = "/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align",
             pattern = "*\\.f0.txt$", full.names = T)

normTimeF <-  list.files(path = "/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align",
             pattern = "*\\.normtimef0.txt$", full.names = T)

read_txt <- function(file) {
  file_name <- basename(file)
  file_name <- str_extract(file_name, "\\S+(?=.txt?)|\\S+(?=.normtimeIntensity?)")
  
  file <- read.csv(file,  sep ="\t", stringsAsFactors = F, header = T)
  file[, "name"] <- file_name
  
  return(file)
}

fZero <- lapply(pitchF, read_txt)
normfZero <- lapply(normTimeF, read_txt)

fZero <- do.call(rbind, fZero)
normZero <- do.call(rbind, normfZero)

# Norm time f0 and f0 do not have the same number of rows...
library(dplyr)
fZero %>%
  group_by(name) %>%
  dplyr::summarise(n = n())

normZero %>%
  group_by(name) %>%
  dplyr::summarise(n = n())


normZero$part_id <- str_extract(normZero$name, "\\S+(?=_r)")
normZero$task <- str_extract(normZero$name, "rsr\\S{1}")


spB$rowLabel <- paste0(spB$vowel, spB$stress)

normZero[which(normZero$rowLabel %in% unique(spB$rowLabel)),]

normZero$stress <- str_extract(normZero$rowLabel, "\\d")
normZero$vowel <- str_remove(normZero$rowLabel, "\\d")
normZero[which(str_detect(normZero$part_id, "blast")), "group"] <- "TD"
normZero[which(str_detect(normZero$part_id, "spoli")), "group"] <- "ASD"


stressed_normZero <-
normZero %>%
    filter(stress == 1, 
           vowel %in% c("IY", "IH", "EY", "EH",  
                                     "AA", "AO", "OW", "UH", "UW", "AH", "AE")) 


normZero %>%
    filter(stress == 1, 
           vowel %in% c("IY", "IH", "EY", "EH",  
                                     "AA", "AO", "OW", "UH", "UW", "AH", "AE")) %>%
  group_by(part_id, task) %>%
  dplyr::summarise(mean(F0))

stressed_normZero %>%
 ggplot(aes(x = task, y = F0)) +
  geom_bar(
    aes(fill = group),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean",
  ) 

stressed_normZero %>%
 ggplot(aes(x = task, y = F0)) +
  geom_bar(
    aes(fill = group),
    position = position_dodge(),
    width = 0.9,
    stat = "summary",
    fun.y = "mean",
  ) + 
    facet_grid(~vowel)

```

# Coarticulation analysis
```{r}
lableList <- list.files(path = "/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align/", 
                        pattern = "normtimeIntensity$", full.names = T)

labelF <- lapply(lableList, read_txt)

labelF <- do.call(rbind, labelF)

# Double check if the cbind matches the rowLabel and the sounds correctly
labeledFzero <- cbind(normZero, labelF[,c("ActualTime", "Intensity")])

labeledFzero <- labeledFzero[which(labeledFzero$stress == 1),] 
  
n = 0

pitchFormant <- list()

for(i in 1:length(unique(labeledFzero$name))) {
  n = n + 1
  iPitch <- labeledFzero[which(labeledFzero$name == unique(labeledFzero$name)[i]),]
  iFormant <- spB[which(spB$part_id == unique(iPitch$part_id) & spB$task == unique(iPitch$task)),]
  
  startRow <- which(iPitch$ActualTime %in% iFormant$beg)
  
  iPitch <- iPitch[c(sapply(startRow, function(x) seq(x, x + 9))),]
  
  pitchFormant[[n]] <- cbind(prosodyPro = iPitch, fave = iFormant[rep(seq_len(nrow(iFormant)), each = 10), ])
  
}

pitchFormant <- do.call(rbind, pitchFormant)

stressed_normZero <-
pitchFormant %>%
    filter(fave.stress == 1, 
           fave.vowel %in% c("IY", "IH", "EY", "EH",  
                                     "AA", "AO", "OW", "UH", "UW", "AH", "AE")) 

pitchWord <- 
stressed_normZero %>%
  group_by(fave.group, fave.task, fave.word, fave.vowel) %>%
  dplyr::summarise(mean(prosodyPro.F0))

stressed_normZero %>%
 ggplot(aes(x = fave.task, y = prosodyPro.F0)) +
  geom_bar(
    aes(fill = fave.word),
    position = position_dodge(width = 0.1),
   
    stat = "summary",
    fun.y = "mean"
  ) + 
  facet_grid(~fave.group)



stressed_normZero[which(stressed_normZero$fave.group == "TD"),] %>%
  ggplot(aes(x = fave.norm_F2, y = fave.norm_F1, color = fave.word)) + 
      geom_point() + 
      scale_x_reverse() + scale_y_reverse() +
      theme_classic() + 
    facet_grid(~fave.task)


stressed_normZero[which(stressed_normZero$fave.group == "ASD"),] %>%
  ggplot(aes(x = fave.norm_F2, y = fave.norm_F1, color = fave.word)) + 
      geom_point() + 
      scale_x_reverse() + scale_y_reverse() +
      theme_classic() + 
    facet_grid(~fave.task)

unique(stressed_normZero$fave.part_id)
```

```{r}
pitchTrackList <- list.files(path = "/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-extract", 
                        pattern = "*pitch_contour_results_hz.csv", full.names = T)

pitchTrackF <- lapply(pitchTrackList, read.csv)

pitchTrackF <- do.call(rbind, pitchTrackF)

colnames(pitchTrackF) <- c("file", "label", "beginT", "duration", 0, 20, 40, 60, 80, 100, "extra")

pitchTrackF <- pitchTrackF[,!colnames(pitchTrackF) %in% "extra"]


pitchTrackF[,c( "beginT", "duration", "0", "20", "40", "60", "80", "100")] <-
  lapply(pitchTrackF[, c("beginT", "duration", "0", "20", "40", "60", "80", "100")], 
         function(x) {
           as.numeric(as.character(x))
  })

pitchTrackF$label <- as.character(pitchTrackF$label)
pitchTrackF$file <- as.character(pitchTrackF$file)

pitchTrackStressed <- pitchTrackF[which(str_detect(pitchTrackF$label, "1")),]



pitchTrackStressed$stressed <- str_extract(pitchTrackStressed$label, "1")
pitchTrackStressed$vowel <- str_remove(pitchTrackStressed$label, "1")
pitchTrackStressed$part_id <- str_extract(pitchTrackStressed$file, "\\S+(?=_rsr)|rsr_orig|new_speaker")
pitchTrackStressed$task <- str_extract(pitchTrackStressed$file, "rsr1|rsr2|rsr_orig|new_speaker")

pitchTrackStressed <-
  merge(stressed_normZero, pitchTrackStressed, by.x = c("fave.part_id", "fave.task", "fave.beg"), 
        by.y = c("part_id", "task", "beginT"), all.x = T)
```


# Check whether below works. Sentence match is already done above.

```{r}
pitchTrack <- rowDiffT[,c("fave.part_id", "fave.task", "vowel", "fave.beg", "sentence_estimate", "0", "20", "40", "60", "80", "100")]

pitchTrackL <- reshape2::melt(pitchTrack, id.vars = c("fave.part_id", "fave.task", "vowel", "fave.beg", "sentence_estimate"))

outlier <- mean(pitchTrackL$value, na.rm = T) + 3*sd(pitchTrackL$value, na.rm = T)

pitchTrackL <- pitchTrackL[-which(pitchTrackL$value > outlier),]

pitchTrackL[which(pitchTrackL$fave.part_id == "blast_c_484" & pitchTrackL$sentence_estimate == 2),] %>%
  ggplot(aes(x = fave.beg, y = value, color = fave.task)) +
  geom_point() +
  geom_line(stat ="summary", fun.y = "mean")





plotPitchTrack <- 
function(part_id, i) {
pitchTrackL[which(pitchTrackL$fave.part_id == part_id & pitchTrackL$sentence_estimate == i),] %>%
  ggplot(aes(x = fave.beg, y = value, color = fave.task)) +
  geom_point() +
  geom_line(stat ="summary", fun.y = "mean")
}



# write.csv(pitchTrackStressed, "/Users/jojohu/Documents/Time/pitchTrackStressed.csv")


```


# Match the sentence numbers
```{r}
read_txt_sentence <- function(file) {
  file_name <- basename(file)
  file_name <- str_extract(file_name, "\\S+(?=.txt?)")
  
  file <- read.csv(file,  sep ="\t", stringsAsFactors = F, header = F)
  file <- file[,1:5]
  file[, "name"] <- file_name
  
  return(file)
}

sentenceF <- list.files(path = "/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align", 
                    pattern = "[0-9][0-9].txt$", full.names = T)

sentenceDF <- list()
tempIndex <- c(1:12, 14:length(sentenceF))
for(i in tempIndex) {
  sentenceDF[[i]] <- read_txt_sentence(sentenceF[i])
}

# This file's encoding has a problem:
tempF <- read.csv("/Users/jojohu/Documents/Time/FAVE-1.2.3/FAVE-align/spoli_c_627_rsr1_mar42021_manual.csv", header = F)
tempF$name <- "spoli_c_627_rsr1_mar42021"

sentenceDF <- do.call(rbind, sentenceDF)

sentenceDF <- rbind(sentenceDF, tempF)

sentenceDF <- sentenceDF[,c(3:6)]
  
colnames(sentenceDF) <- c("sentence_beg", "sentence_end", "sentence", "file")


```


